---
title: "microfims_merge_datasets"
output: html_document
date: "2024-03-26"
author: Fran Querdasi
---
test
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup
## Load libraries
```{r}
library(tidyverse)
library(haven)
```

## Load data
Demographics, ID to secondary ID key, microFIMS, macroFIMS, CBCL w1, BDI w1, coders' data, microFIMS tiebreakers, TESI total count
```{r}
demo_microfims <- read_csv("../Wave_1/Data_scoring/demographics_parentproxy/demographics_clean_w1.csv") %>% dplyr::select(
  participant_id,
  family_id,
  ELA_group_w1,
  ELA_subgroup_str_w1,
  child_age_years_w1,
  child_sex_w1,
  child_gender_w1,
  child_race_w1,
  primarycaregiver_race_w1,
  secondarycaregiver_race_w1,
  demographics_respondent_w1,
  primary_caregiver_w1,
  secondary_caregiver_w1,
  respondent_gender_w1,
  primary_caregiver_gender_w1,
  secondary_caregiver_gender_w1
)

id_key <- read_csv("../../ID_drive/ID_MBB_secondary.csv") %>% dplyr::rename(participant_id = primary_id)

microfims_child <- read_csv("../../FIMS/FIMS_micro_coding/MicroFIMS Core Team Training/microFIMS_reliability_data/behavior/child_summary_each_p.csv")

microfims_parent <- read_csv("../../FIMS/FIMS_micro_coding/MicroFIMS Core Team Training/microFIMS_reliability_data/behavior/parent_summary_each_p.csv")

cbcl_microfims <- read_csv("../Wave_1/Data_scoring/Cbcl/cbcl_dsm_mean_scores.csv")

bdi_microfims <- read_csv("../Wave_1/Data_scoring/bdi_ii/bdi_scores_items_w1_20240421.csv") %>% dplyr::select(
  participant_id:bdi_ii_parentselfreport_18
)

w1_inperson <- read_csv("../Wave_1/Data_clean/wave_1_in_person_data_clean.csv") %>% dplyr::select(participant_id) %>% dplyr::mutate(w1_inperson = 1)

macrofims <- read_sav("../../../../Users/Jenn/APIM - revised w mental health/MBB FIMS final both tasks v7.sav") %>% dplyr::select(
   participant_id,
   secondary_id,
   involve_task_mother_positive:conflict_level_positive,
   involve_task_mother_negative:conflict_level_negative
   #maybe also a few calculated vars -- decided no:
   #affect_child_positive:childposdiff
)

coders_microfims <- readxl::read_xlsx("data/Micro FIMS Check-list (Responses)_EDITED.xlsx") %>% dplyr::filter(is.na(`I coded:`)) %>% dplyr::select(
  secondary_id = `The video you coded:\r\n\r\n* type the last 3 digits after MBB_2_### below (e.g. for MBB_2_001 write 001)`,
  dyad_member = `The role:`,
  time_spent_coding = `How long did it take you to complete this video (in minutes) (e.g., 60, 90)`,
  coder_likeability = `How likable is this person to you:`,
  coder_familiarity = `How familiar is this person to you:`
)

pgender_microfims <- readxl::read_xlsx("data/MBB Transcription Tracker.xlsx") %>% dplyr::select(
   secondary_id = ID,
   parent_perceived_gender = `Parent Perceived Gender`
 ) %>% dplyr::mutate(
   parent_perceived_gender = case_when(parent_perceived_gender=="Female" ~ "woman",
                                       parent_perceived_gender=="Male" ~ "man")
 )

# microfims tiebreakers
tiebreak_microfims_child <- read_csv("../../FIMS/FIMS_micro_coding/MicroFIMS Core Team Training/microFIMS_reliability_data/behavior/tiebreaker_data/child_summary_each_p_tiebreakers.csv")

tiebreak_microfims_parent <- read_csv("../../FIMS/FIMS_micro_coding/MicroFIMS Core Team Training/microFIMS_reliability_data/behavior/tiebreaker_data/parent_summary_each_p_tiebreakers.csv")

# microfims consensus code base rates
cons_microfims_child <- read_csv("../../FIMS/FIMS_micro_coding/MicroFIMS Core Team Training/microFIMS_cerfication_data/microFIMS_certification_behavior/child_baserates_cons.csv") %>% dplyr::rename(secondary_id = participant)
cons_microfims_parent <- read_csv("../../FIMS/FIMS_micro_coding/MicroFIMS Core Team Training/microFIMS_cerfication_data/microFIMS_certification_behavior/parent_baserates_cons.csv") %>% dplyr::rename(secondary_id = participant)

# tesi
tesi <- read_csv("../Wave_1/Data_scoring/tesi_parentproxy/tesi_parentproxy_w1_20240402.csv") %>% dplyr::select(participant_id, tesi_anyadversity_binary_w1)
```

# Clean individual datasets
## CBCL
Replace mean scores with NA if >30% missing on each subscale
```{r}
# Find columns ending in "_row_means" and "_prcnt_complete"
row_means_cols <- grep("_row_means$", names(cbcl_microfims), value = TRUE)
prcnt_complete_cols <- grep("_prcnt_complete$", names(cbcl_microfims), value = TRUE)

# Loop through each pair of columns
for (i in 1:length(row_means_cols)) {
  row_means_col <- row_means_cols[i]
  prcnt_complete_col <- prcnt_complete_cols[grep(sub("_row_means$", "", row_means_col), prcnt_complete_cols)]
  
  # Replace values with NA where percentage complete is less than 70
  cbcl_microfims[cbcl_microfims[[prcnt_complete_col]] < .7, row_means_col] <- NA
}
```

## BDI
Create mean scores and % complete with only original items 2-21
```{r}
#create dataset that is subset of vars to be counted
bdi_vars_d <- 
  bdi_microfims %>% 
  select(bdi_ii_parentselfreport_2:bdi_ii_parentselfreport_18) 

# create new vars
bdi_microfims <- bdi_microfims %>% 
  dplyr::mutate(
    bdi_sum_w1 = rowSums(bdi_vars_d, na.rm=TRUE),
    bdi_qs_answered = rowSums(!is.na(bdi_vars_d)),
    bdi_mean_score_w1 = bdi_sum_w1/bdi_qs_answered,
    bdi_pct_complete_w1 = bdi_qs_answered/20
  )

# if bdi pct complete < 70, change mean score to be NA
bdi_microfims<- bdi_microfims %>% 
  dplyr::mutate(
    bdi_mean_score_w1 = ifelse(bdi_pct_complete_w1 < .7, NA, bdi_mean_score_w1)
  )

# remove vars we don't need
bdi_microfims_clean <- bdi_microfims %>% dplyr::select(participant_id, bdi_mean_score_w1, bdi_pct_complete_w1)
```

## MicroFIMS
add _child or _parent to columns in each dataset, remove _parent and _child from secondary id, rename 'participant' --> secondary_id
create flag for low kappa and >50% uncodable
Add secondary ID to ID key
Add interaction: PSI
Then merge the datasets
```{r}
# CHILD DATASET
# remove columns that we don't care about (prescence_agree, kappa besides total)
microfims_child_clean <- microfims_child %>% dplyr::select(
  participant,
  contains("percent_agree"),
  contains("baserate"),
  total_kappa_child,
  contains("seconds_coded"),
  coder1_child,
  coder2_child
)

# add _child to all columns (commented out bc most recent version of file will alraedy have these)
# colnames(microfims_child_clean) <-  paste(colnames(microfims_child_clean), "child", sep="_")
# 
# microfims_child_clean <- microfims_child_clean %>% 
#   rename(participant = participant_child)

# remove _child from id
microfims_child_clean$participant <- gsub("_child", "", microfims_child_clean$participant)

# rename 'participant' to secondary_id, add interaction = PSI variable, merge with secondary ID key
microfims_child_clean <- microfims_child_clean %>% 
  dplyr::rename(secondary_id = participant) %>% 
  dplyr::mutate(microfims_interaction = "PSI") %>% 
  dplyr::left_join(id_key, by = "secondary_id") %>% 
  dplyr::select(
    participant_id,
    secondary_id, 
    everything()
  )

# create flags: low kappa, high % uncodable
microfims_child_clean <- microfims_child_clean %>% 
  dplyr::mutate(
    low_kappa_flag_child = ifelse(total_kappa_child < 0.4, 1, 0),
    high_uncodable_flag_child = ifelse(baserate_uncodable_coder1_child > .5 | baserate_uncodable_coder2_child > .5, 1, 0)
  )

# PARENTS DATASET
microfims_parent_clean <- microfims_parent %>% dplyr::select(
  participant,
  contains("percent_agree"),
  contains("baserate"),
  total_kappa_parent,
  contains("seconds_coded"),
  coder1_parent,
  coder2_parent
)

# add _parent to all columns (commented out bc most recent version of file will alraedy have these)
# colnames(microfims_parent_clean) <-  paste(colnames(microfims_parent_clean), "parent", sep="_")
# 
# microfims_parent_clean <- microfims_parent_clean %>% 
#   rename(participant = participant_parent)

# remove _parent from id
microfims_parent_clean$participant <- gsub("_parent", "", microfims_parent_clean$participant)

# rename 'participant' to secondary_id, merge with secondary ID key
microfims_parent_clean <- microfims_parent_clean %>% 
  dplyr::rename(secondary_id = participant) %>% 
  dplyr::left_join(id_key, by = "secondary_id") %>% 
  dplyr::select(
    participant_id,
    secondary_id, 
    everything()
  )

microfims_parent_clean <- microfims_parent_clean %>% 
  dplyr::mutate(
    low_kappa_flag_parent = ifelse(total_kappa_parent < 0.4, 1, 0),
    high_uncodable_flag_parent = ifelse(baserate_uncodable_coder1_parent > .5 | baserate_uncodable_coder2_parent > .5, 1, 0)
  )

# merge parent and child datasets
microfims_clean <- microfims_child_clean %>% dplyr::full_join(microfims_parent_clean, by = c("participant_id", "secondary_id")) 

# rename variables with _codable to be <code>_proportion (will take out once fix reliability scripts to give correct name)
microfims_clean <- microfims_clean %>% dplyr::rename_with(., ~gsub("baserate_codable_", "proportion_", .x), contains("_codable_"))

# remove the proportion_codable columns
microfims_clean <- microfims_clean %>% dplyr::select(-contains("proportion_uncodable"))

# change MBB_2_095 and MBB_2_137 total kappa to be 1 (because % agreement is 100, both coders rated entire video as uncodable)
microfims_clean[which(microfims_clean$secondary_id=="MBB_2_137"), "total_kappa_child"] <- 1
microfims_clean[which(microfims_clean$secondary_id=="MBB_2_095"), "total_kappa_child"] <- 1
microfims_clean[which(microfims_clean$secondary_id=="MBB_2_137"), "total_kappa_parent"] <- 1
microfims_clean[which(microfims_clean$secondary_id=="MBB_2_095"), "total_kappa_parent"] <- 1
```

### Add tiebreaker base rates
```{r}
# CHILD TIEBREAKERS
# add _child to all columns
colnames(tiebreak_microfims_child) <-  paste(colnames(tiebreak_microfims_child), "child", sep="_")

tiebreak_microfims_child <- tiebreak_microfims_child %>% 
  rename(participant = participant_child)

# remove _child from id
tiebreak_microfims_child$participant <- gsub("_child", "", tiebreak_microfims_child$participant)

# rename 'participant' to secondary_id, add interaction = PSI variable, merge with secondary ID key
tiebreak_microfims_child <- tiebreak_microfims_child %>% 
  dplyr::rename(secondary_id = participant) %>% 
  dplyr::left_join(id_key, by = "secondary_id") %>% 
  dplyr::select(
    participant_id,
    secondary_id, 
    everything()
  )

# PARENT TIEBREAKERS
# add _parent to all columns
colnames(tiebreak_microfims_parent) <-  paste(colnames(tiebreak_microfims_parent), "parent", sep="_")

tiebreak_microfims_parent <- tiebreak_microfims_parent %>% 
  rename(participant = participant_parent)

# remove _parent from id
tiebreak_microfims_parent$participant <- gsub("_parent", "", tiebreak_microfims_parent$participant)

# rename 'participant' to secondary_id, merge with secondary ID key
tiebreak_microfims_parent <- tiebreak_microfims_parent %>% 
  dplyr::rename(secondary_id = participant) %>% 
  dplyr::left_join(id_key, by = "secondary_id") %>% 
  dplyr::select(
    participant_id,
    secondary_id, 
    everything()
  )

# merge parent and child datasets
tiebreak_microfims_clean <- tiebreak_microfims_parent %>% dplyr::full_join(tiebreak_microfims_child, by = c("participant_id", "secondary_id"))
```

### Add base rates from certification videos
```{r}
# CHILD CONSENSUS
# add _child to all columns
colnames(cons_microfims_child) <-  paste(colnames(cons_microfims_child), "child", sep="_")

cons_microfims_child <- cons_microfims_child %>% 
  rename(secondary_id = secondary_id_child)

# remove _child from id
cons_microfims_child$secondary_id <- gsub("_child", "", cons_microfims_child$secondary_id)

# PARENT CONSENSUS
# add _parent to all columns
colnames(cons_microfims_parent) <-  paste(colnames(cons_microfims_parent), "parent", sep="_")

cons_microfims_parent <- cons_microfims_parent %>% 
  rename(secondary_id = secondary_id_parent)

# remove _parent from id
cons_microfims_parent$secondary_id <- gsub("_parent", "", cons_microfims_parent$secondary_id)

# merge parent and child datasets
cons_microfims_clean <- cons_microfims_parent %>% dplyr::full_join(cons_microfims_child, by = "secondary_id")
```

## Demographics
Add variable for W1 in person vs remote
*may change this bc currently it just gives everyone 0 who didn't participate in in-person, even some people who didn't participate at all*
```{r}
# merge demographics with w1 inperson variable
demo_microfims_clean <- demo_microfims %>% left_join(w1_inperson, by = "participant_id") %>% dplyr::mutate(
  w1_inperson = ifelse(is.na(w1_inperson), 0, w1_inperson)
)

# remove demo person who isn't in sample
demo_microfims_clean <- demo_microfims_clean %>% dplyr::filter(participant_id != "MBB434")
```

## Coders' data
```{r}
# standardize the ids -- get MBB_2_002_XXX for everyone
coders_microfims$secondary_id <- gsub("MBB_2_", "", coders_microfims$secondary_id)

coders_microfims <- coders_microfims %>% dplyr::mutate(
  secondary_id = ifelse(nchar(secondary_id) == 2, paste0("0", secondary_id), secondary_id),
  secondary_id = ifelse(nchar(secondary_id) == 1, paste0("00", secondary_id), secondary_id)
)

coders_microfims$secondary_id <- coders_microfims$secondary_id <- paste0("MBB_2_", coders_microfims$secondary_id)

# map the duplicate coder values into three columns: coder_likeability_a, coder_likeability_b, coder_likeability_c

# for some reason there is an extra row for MBB_2_018 parent with time spent coding equal to 45 min; not sure where it comes frrom in the excel sheet but confirmed it is not the correct 2 lines
coders_microfims <- coders_microfims %>% dplyr::filter(!(secondary_id=="MBB_2_018" & time_spent_coding == "45"))

coders_microfims_pivot <- coders_microfims %>% 
  group_by(secondary_id, dyad_member) %>%
  mutate(new_variable = case_when(
    row_number() == 1 ~ 'a',
    row_number() == 2 ~ 'b'
    #row_number() == 3 ~ 'c',
    #row_number() == 4 ~ 'd'
  )
  )
           
# move from long to wide, with _parent or _child appended to likeability and familiarity variables
coders_micro_wide <- coders_microfims_pivot %>% pivot_wider(
                         id_cols = secondary_id,
                         names_from = c(dyad_member, new_variable),
                         values_from = c(time_spent_coding, coder_likeability, coder_familiarity),
                         names_sep = "_")
```

# Merge the datasets
## Reliability
Demographics, all microfims, coders'
use macrofims IDs as left join
```{r}
reliability_microfims <- macrofims %>% dplyr::select(participant_id) %>% dplyr::left_join(demo_microfims_clean, by = "participant_id") %>% dplyr::left_join(microfims_clean, by = "participant_id") %>% dplyr::left_join(coders_micro_wide, by = "secondary_id") %>% dplyr::left_join(pgender_microfims, by = "secondary_id")

# create a flag variable for whether questionnaire respondent gender matches perceived gender from video
reliability_microfims <- reliability_microfims %>% dplyr::mutate(
  caregiver_gender_mismatch_flag = ifelse(parent_perceived_gender==respondent_gender_w1, 0, 1)
)

#examine 2_095 and 2_137 (entire video was 'uncodable')
#test_reliability_microfims <- reliability_microfims %>% dplyr::filter(secondary_id=="MBB_2_095" | secondary_id=="MBB_2_137")

# check on missing participants
#ids_with_na_kappa <- subset(reliability_microfims, is.na(total_kappa_parent))$participant_id

# add low kappa and high uncodable flags = 0 for certification videos and 2_095 and 2_137 (entire video was 'uncodable')
reliability_microfims <- reliability_microfims %>% dplyr::mutate(
  low_kappa_flag_parent = ifelse(secondary_id %in% c("MBB_2_095", "MBB_2_137", "MBB_2_005", "MBB_2_144", "MBB_2_036"), 0, low_kappa_flag_parent),
  low_kappa_flag_child = ifelse(secondary_id %in% c("MBB_2_095", "MBB_2_137", "MBB_2_005", "MBB_2_144", "MBB_2_036"), 0, low_kappa_flag_child),
  high_uncodable_flag_child = ifelse(secondary_id %in% c("MBB_2_095", "MBB_2_137", "MBB_2_005", "MBB_2_144", "MBB_2_036"), 0, high_uncodable_flag_child),
  high_uncodable_flag_parent = ifelse(secondary_id %in% c("MBB_2_095", "MBB_2_137", "MBB_2_005", "MBB_2_144", "MBB_2_036"), 0, high_uncodable_flag_parent),
)

#exclude 2_030 and 2_052 (did not have task data)
reliability_microfims_final <- reliability_microfims %>% dplyr::filter(!(participant_id %in% c("MBB141", "MBB035")))
```

## Validity
Demographics, microFIMS base rates, macrofims, cbcl, bdi, tesi
```{r}
# select only base rates from microfims
microfims_validity <- microfims_clean %>% dplyr::select(participant_id, secondary_id, contains("proportion"), contains("kappa"), contains("flag")) %>% dplyr::filter(!is.na(participant_id))

# randomly assign one coder to be 'primary' for each video
primary_coder <- replicate(nrow(microfims_validity), sample(c("coder1", "coder2"), 1))

# bind primary coder column to rest of dataset
microfims_validity <- cbind(microfims_validity, primary_coder)

# duplicate the base rates for the assigned primary coder and call them "_primary" 
# extract the substrings of the variables
first_substring <- substrings <- unique(gsub("_coder[12].*", "", names(microfims_validity)[-1]))[2:8]
second_substring <- unique(gsub(".*_coder[12]_", "", names(microfims_validity)[-1]))[2:3]

#Loop over substrings and create corresponding "primary" columns
for (i in 1:nrow(microfims_validity)) {
for (substring in first_substring) {
  for (substring2 in second_substring) {
  coder1_col <- paste0(substring, "_coder1_", substring2)
  coder2_col <- paste0(substring, "_coder2_", substring2)
  primary_col <- paste0(substring, "_primary_", substring2)
  
  microfims_validity[i, primary_col] <- ifelse(microfims_validity$primary_coder[i] == "coder1", microfims_validity[i, coder1_col], microfims_validity[i, coder2_col])
  }
}
}

# remove columns with coder1 and coder2, merge with tiebreaker base rates
microfims_validity_merge <- microfims_validity %>% dplyr::select(-contains("coder1"), -contains("coder2")) %>% dplyr::left_join(tiebreak_microfims_clean, by = c("participant_id", "secondary_id"))

# replace primary base rates with tiebreakers for those with low kappa
for (i in 1:nrow(microfims_validity_merge)) {
for (substring in first_substring) {
  for (substring2 in second_substring) {
  primary_col <- paste0(substring, "_primary_", substring2)
  final_col <- paste0(substring, "_final_", substring2)
  low_kappa_flag_col <- paste0("low_kappa_flag_", substring2)
  
  microfims_validity_merge[i, primary_col] <- ifelse(microfims_validity_merge[[low_kappa_flag_col]][i] == "1", microfims_validity_merge[i, final_col], microfims_validity_merge[i, primary_col]) 
  }
}
}

# merge the rest of the data
validity_microfims <- macrofims %>% dplyr::select(participant_id, secondary_id) %>% dplyr::left_join(demo_microfims_clean, by =  "participant_id") %>% dplyr::left_join(microfims_validity %>% dplyr::select(-secondary_id), by = "participant_id") %>% dplyr::left_join(macrofims %>% dplyr::select(-secondary_id), by = "participant_id") %>% dplyr::left_join(cbcl_microfims, by = "participant_id") %>% dplyr::left_join(bdi_microfims_clean, by = "participant_id")

# create a flag for participants for whom consensus codes should be used for base rates
validity_microfims <- validity_microfims %>% dplyr::mutate(
  use_certif_codes_flag = ifelse(secondary_id %in% c("MBB_2_005", "MBB_2_036", "MBB_2_144"), 1, 0)
)

# merge the consensus code columns
validity_microfims <- validity_microfims %>% dplyr::left_join(cons_microfims_clean, by = "secondary_id")

# replace the 'primary' base rates with consesus code base rates...
for (i in 1:nrow(validity_microfims)) {
for (substring in first_substring) {
  for (substring2 in second_substring) {
  primary_col <- paste0(substring, "_primary_", substring2)
  cons_col <- paste0(substring, "_cons_", substring2)
  
  validity_microfims[i, primary_col] <- ifelse(validity_microfims[["use_certif_codes_flag"]][i] == "1", validity_microfims[i, cons_col], validity_microfims[i, primary_col])  
  }
}
}

# get rid of coder1, coder2, and cons columns
validity_microfims_final <- validity_microfims %>% dplyr::select(-contains("_coder1_"), -contains("_coder2_"), -contains("_cons_"))

#exclude 2_030 and 2_052 (did not have task data)
validity_microfims_final <- validity_microfims_final %>% dplyr::filter(!(secondary_id %in% c("MBB_2_030", "MBB_2_052")))

# add questionnaire and interaction gender matches from reliability dataset
validity_microfims_final <- validity_microfims_final %>% dplyr::left_join(reliability_microfims %>% dplyr::select(participant_id, parent_perceived_gender, caregiver_gender_mismatch_flag), by = "participant_id")

# add low kappa and high uncodable flags = 0 for certification videos and 2_095 and 2_137 (entire video was 'uncodable')
validity_microfims_final <- validity_microfims_final %>% dplyr::mutate(
  low_kappa_flag_parent = ifelse(secondary_id %in% c("MBB_2_095", "MBB_2_137", "MBB_2_005", "MBB_2_144", "MBB_2_036"), 0, low_kappa_flag_parent),
  low_kappa_flag_child = ifelse(secondary_id %in% c("MBB_2_095", "MBB_2_137", "MBB_2_005", "MBB_2_144", "MBB_2_036"), 0, low_kappa_flag_child),
  high_uncodable_flag_child = ifelse(secondary_id %in% c("MBB_2_095", "MBB_2_137", "MBB_2_005", "MBB_2_144", "MBB_2_036"), 0, high_uncodable_flag_child),
  high_uncodable_flag_parent = ifelse(secondary_id %in% c("MBB_2_095", "MBB_2_137", "MBB_2_005", "MBB_2_144", "MBB_2_036"), 0, high_uncodable_flag_parent),
)

# add tesi yes/no adversity variable
validity_microfims_final <- validity_microfims_final %>% dplyr::left_join(tesi, by = "participant_id")
```

# Output the datasets
Consider where to output these files
```{r}
write_csv(reliability_microfims_final, "data/microfims_reliability_final_data.csv")

write_csv(validity_microfims_final, "data/microfims_validity_final_data_testing.csv")
```

# Investigate missing microfims
```{r}
# get secondary id
# macrofims_ids <- read_sav("../../../../Users/Jenn/APIM - revised w mental health/MBB FIMS final both tasks v7.sav") %>% dplyr::select(
#    participant_id,
#    secondary_id
# )
# 
# microfims_missing_ids <- reliability_microfims %>% dplyr::filter(is.na(secondary_id)) %>% dplyr::select(participant_id) %>% dplyr::left_join(macrofims_ids, by = "participant_id")
```

