---
title: "microfims_merge_datasets"
output: html_document
date: "2024-03-26"
author: Fran Querdasi
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup
## Load libraries
```{r}
library(tidyverse)
library(haven)
```

## Load data
Demographics, ID to secondary ID key, microFIMS, macroFIMS, CBCL w1, BDI w1, coders' data, microFIMS tiebreakers
```{r}
demo_microfims <- read_csv("../Wave_1/Data_scoring/demographics_parentproxy/demographics_clean_w1.csv") %>% dplyr::select(
  participant_id,
  family_id,
  ELA_group_w1,
  ELA_subgroup_str_w1,
  child_age_years_w1,
  child_sex_w1,
  child_gender_w1,
  child_race_w1,
  primarycaregiver_race_w1,
  secondarycaregiver_race_w1,
  demographics_respondent_w1,
  primary_caregiver_w1,
  secondary_caregiver_w1,
  respondent_gender_w1,
  primary_caregiver_gender_w1,
  secondary_caregiver_gender_w1
)

id_key <- read_csv("../../ID_drive/ID_MBB_secondary.csv") %>% dplyr::rename(participant_id = primary_id)

microfims_child <- read_csv("../../FIMS/FIMS_micro_coding/MicroFIMS Core Team Training/microFIMS_reliability_data/behavior/child_summary_each_p.csv")

microfims_parent <- read_csv("../../FIMS/FIMS_micro_coding/MicroFIMS Core Team Training/microFIMS_reliability_data/behavior/parent_summary_each_p.csv")

cbcl_microfims <- read_csv("../Wave_1/Data_scoring/Cbcl/cbcl_dsm_mean_scores.csv")

bdi_microfims <- read_csv("../Wave_1/Data_scoring/bdi_ii/bdi_scores_items_w1_20221031.csv") %>% dplyr::select(
  participant_id:bdi_ii_parentselfreport_18
)

w1_inperson <- read_csv("../Wave_1/Data_clean/wave_1_in_person_data_clean.csv") %>% dplyr::select(participant_id) %>% dplyr::mutate(w1_inperson = 1)

macrofims <- read_sav("../../../../Users/Jenn/APIM - revised w mental health/MBB FIMS final both tasks v7.sav") %>% dplyr::select(
   participant_id,
   involve_task_mother_positive:conflict_level_positive,
   involve_task_mother_negative:conflict_level_negative
   #maybe also a few calculated vars -- decided no:
   #affect_child_positive:childposdiff
)

#coders_microfioms <- 

# microfims tiebreakers
tiebreak_microfims_child <- read_csv("../../FIMS/FIMS_micro_coding/MicroFIMS Core Team Training/microFIMS_reliability_data/behavior/child_summary_each_p_tiebreakers.csv")

tiebreak_microfims_parent <- read_csv("../../FIMS/FIMS_micro_coding/MicroFIMS Core Team Training/microFIMS_reliability_data/behavior/parent_summary_each_p_tiebreakers.csv")
```

# Clean individual datasets
## CBCL
Replace mean scores with NA if >30% missing on each subscale
```{r}
# Find columns ending in "_row_means" and "_prcnt_complete"
row_means_cols <- grep("_row_means$", names(cbcl_microfims), value = TRUE)
prcnt_complete_cols <- grep("_prcnt_complete$", names(cbcl_microfims), value = TRUE)

# Loop through each pair of columns
for (i in 1:length(row_means_cols)) {
  row_means_col <- row_means_cols[i]
  prcnt_complete_col <- prcnt_complete_cols[grep(sub("_row_means$", "", row_means_col), prcnt_complete_cols)]
  
  # Replace values with NA where percentage complete is less than 70
  cbcl_microfims[cbcl_microfims[[prcnt_complete_col]] < .7, row_means_col] <- NA
}
```

## BDI
Create mean scores and % complete with only original items 2-21
```{r}
#create dataset that is subset of vars to be counted
bdi_vars_d <- 
  bdi_microfims %>% 
  select(bdi_ii_parentselfreport_2:bdi_ii_parentselfreport_18) 

# create new vars
bdi_microfims <- bdi_microfims %>% 
  dplyr::mutate(
    bdi_sum_w1 = rowSums(bdi_vars_d, na.rm=TRUE),
    bdi_qs_answered = rowSums(!is.na(bdi_vars_d)),
    bdi_mean_score_w1 = bdi_sum_w1/bdi_qs_answered,
    bdi_pct_complete_w1 = bdi_qs_answered/20
  )

# if bdi pct complete < 70, change mean score to be NA
bdi_microfims<- bdi_microfims %>% 
  dplyr::mutate(
    bdi_mean_score_w1 = ifelse(bdi_pct_complete_w1 < .7, NA, bdi_mean_score_w1)
  )

# remove vars we don't need
bdi_microfims_clean <- bdi_microfims %>% dplyr::select(participant_id, bdi_mean_score_w1, bdi_pct_complete_w1)
```

## MicroFIMS
add _child or _parent to columns in each dataset, remove _parent and _child from secondary id, rename 'participant' --> secondary_id
create flag for low kappa and >50% uncodable
Add secondary ID to ID key
Add interaction: PSI
Then merge the datasets
```{r}
# CHILD DATASET
# remove columns that we don't care about (prescence_agree, kappa besides total)
microfims_child_clean <- microfims_child %>% dplyr::select(
  participant,
  contains("percent_agree"),
  contains("baserate"),
  total_kappa,
  coder1,
  coder2
)

# add _child to all columns
colnames(microfims_child_clean) <-  paste(colnames(microfims_child_clean), "child", sep="_")

microfims_child_clean <- microfims_child_clean %>% 
  rename(participant = participant_child)

# remove _child from id
microfims_child_clean$participant <- gsub("_child", "", microfims_child_clean$participant)

# rename 'participant' to secondary_id, add interaction = PSI variable, merge with secondary ID key
microfims_child_clean <- microfims_child_clean %>% 
  dplyr::rename(secondary_id = participant) %>% 
  dplyr::mutate(microfims_interaction = "PSI") %>% 
  dplyr::left_join(id_key, by = "secondary_id") %>% 
  dplyr::select(
    participant_id,
    secondary_id, 
    everything()
  )

# create flags: low kappa, high % uncodable
microfims_child_clean <- microfims_child_clean %>% 
  dplyr::mutate(
    low_kappa_flag_child = ifelse(total_kappa_child < 0.4, 1, 0),
    high_uncodable_flag_child = ifelse(baserate_uncodable_coder1_child > .5 | baserate_uncodable_coder2_child > .5, 1, 0)
  )

# PARENTS DATASET
microfims_parent_clean <- microfims_parent %>% dplyr::select(
  participant,
  contains("percent_agree"),
  contains("baserate"),
  total_kappa,
  coder1,
  coder2
)

# add _parent to all columns
colnames(microfims_parent_clean) <-  paste(colnames(microfims_parent_clean), "parent", sep="_")

microfims_parent_clean <- microfims_parent_clean %>% 
  rename(participant = participant_parent)

# remove _child from id
microfims_parent_clean$participant <- gsub("_parent", "", microfims_parent_clean$participant)

# rename 'participant' to secondary_id, merge with secondary ID key
microfims_parent_clean <- microfims_parent_clean %>% 
  dplyr::rename(secondary_id = participant) %>% 
  dplyr::left_join(id_key, by = "secondary_id") %>% 
  dplyr::select(
    participant_id,
    secondary_id, 
    everything()
  )

microfims_parent_clean <- microfims_parent_clean %>% 
  dplyr::mutate(
    low_kappa_flag_parent = ifelse(total_kappa_parent < 0.4, 1, 0),
    high_uncodable_flag_parent = ifelse(baserate_uncodable_coder1_parent > .5 | baserate_uncodable_coder2_parent > .5, 1, 0)
  )

# merge parent and child datasets
microfims_clean <- microfims_child_clean %>% dplyr::full_join(microfims_parent_clean, by = c("participant_id", "secondary_id"))
```

### Add tiebreaker base rates
```{r}
# CHILD TIEBREAKERS
# add _child to all columns
colnames(tiebreak_microfims_child) <-  paste(colnames(tiebreak_microfims_child), "child", sep="_")

tiebreak_microfims_child <- tiebreak_microfims_child %>% 
  rename(participant = participant_child)

# remove _child from id
tiebreak_microfims_child$participant <- gsub("_child", "", tiebreak_microfims_child$participant)

# rename 'participant' to secondary_id, add interaction = PSI variable, merge with secondary ID key
tiebreak_microfims_child <- tiebreak_microfims_child %>% 
  dplyr::rename(secondary_id = participant) %>% 
  dplyr::left_join(id_key, by = "secondary_id") %>% 
  dplyr::select(
    participant_id,
    secondary_id, 
    everything()
  )

# PARENT TIEBREAKERS
# add _parent to all columns
colnames(tiebreak_microfims_parent) <-  paste(colnames(tiebreak_microfims_parent), "parent", sep="_")

tiebreak_microfims_parent <- tiebreak_microfims_parent %>% 
  rename(participant = participant_parent)

# remove _parent from id
tiebreak_microfims_parent$participant <- gsub("_parent", "", tiebreak_microfims_parent$participant)

# rename 'participant' to secondary_id, merge with secondary ID key
tiebreak_microfims_parent <- tiebreak_microfims_parent %>% 
  dplyr::rename(secondary_id = participant) %>% 
  dplyr::left_join(id_key, by = "secondary_id") %>% 
  dplyr::select(
    participant_id,
    secondary_id, 
    everything()
  )

# merge parent and child datasets
tiebreak_microfims_clean <- tiebreak_microfims_parent %>% dplyr::full_join(tiebreak_microfims_child, by = c("participant_id", "secondary_id"))
```

## Demographics
Add variable for W1 in person vs remote
*may change this bc currently it just gives everyone 0 who didn't participate in in-person, even some people who didn't participate at all*
```{r}
# merge demographics with w1 inperson variable
demo_microfims_clean <- demo_microfims %>% left_join(w1_inperson, by = "participant_id") %>% dplyr::mutate(
  w1_inperson = ifelse(is.na(w1_inperson), 0, w1_inperson)
)

# remove demo person who isn't in sample
demo_microfims_clean <- demo_microfims_clean %>% dplyr::filter(participant_id != "MBB434")
```

## Coders'
TBD
```{r}

```

# Merge the datasets
## Reliability
Demographics, all microfims, coders'
use macrofims IDs as left join
```{r}
reliability_microfims <- macrofims %>% dplyr::select(participant_id) %>% dplyr::left_join(demo_microfims_clean, by = "participant_id") %>% dplyr::left_join(microfims_clean, by = "participant_id")
#%>% dplyr::left_join(coders, by = "participant_id")
```

## Validity
Demographics, microFIMS base rates, macrofims, cbcl, bdi
```{r}
# select only base rates from microfims
microfims_validity <- microfims_clean %>% dplyr::select(participant_id, secondary_id, contains("baserate"), contains("flag")) %>% dplyr::filter(!is.na(participant_id))

# randomly assign one coder to be 'master' for each video
master_coder <- replicate(nrow(microfims_validity), sample(c("coder1", "coder2"), 1))

# bind master coder column to rest of dataset
microfims_validity <- cbind(microfims_validity, master_coder)

# duplicate the base rates for the assigned master coder and call them "_master"
# extract the substrings of the variables
first_substring <- substrings <- unique(gsub("_coder[12].*", "", names(microfims_validity)[-1]))[2:17]
second_substring <- unique(gsub(".*_coder[12]_", "", names(microfims_validity)[-1]))[2:3]

#Loop over substrings and create corresponding "master" columns
for (i in 1:nrow(microfims_validity)) {
for (substring in first_substring) {
  for (substring2 in second_substring) {
  coder1_col <- paste0(substring, "_coder1_", substring2)
  coder2_col <- paste0(substring, "_coder2_", substring2)
  master_col <- paste0(substring, "_master_", substring2)
  
  microfims_validity[i, master_col] <- ifelse(microfims_validity$master_coder[i] == "coder1", microfims_validity[i, coder1_col], microfims_validity[i, coder2_col])
  }
}
}

# remove columns with coder1 and coder2, merge with tiebreaker base rates
microfims_validity_merge <- microfims_validity %>% dplyr::select(-contains("coder1"), -contains("coder2")) %>% dplyr::left_join(tiebreak_microfims_clean, by = c("participant_id", "secondary_id"))

# replace master base rates with tiebreakers for those with low kappa
for (i in 1:nrow(microfims_validity_merge)) {
for (substring in first_substring) {
  for (substring2 in second_substring) {
  master_col <- paste0(substring, "_master_", substring2)
  final_col <- paste0(substring, "_final_", substring2)
  low_kappa_flag_col <- paste0("low_kappa_flag_", substring2)
  
  microfims_validity_merge[i, master_col] <- ifelse(microfims_validity_merge[[low_kappa_flag_col]][i] == "1", microfims_validity_merge[i, final_col], microfims_validity_merge[i, master_col]) # need to finish this -- change master_code to "low_kappa_flag_child" or "low_kappa_flag_parent" 
  }
}
}

# merge the rest of the data
validity_microfims <- macrofims %>% dplyr::select(participant_id) %>% dplyr::left_join(demo_microfims_clean, by = "participant_id") %>% dplyr::left_join(microfims_validity, by = "participant_id") %>% dplyr::left_join(macrofims, by = "participant_id") %>% dplyr::left_join(cbcl_microfims, by = "participant_id") %>% dplyr::left_join(bdi_microfims_clean, by = "participant_id")
```

# Output the datasets
Consider where to output these files
```{r}
#write_csv(reliability_microfims, "microfims_reliability_data.csv")

#write_csv(validity_microfims, "microfims_validity_data.csv")
```

# Investigate missing microfims
```{r}
# get secondary id
macrofims_ids <- read_sav("../../../../Users/Jenn/APIM - revised w mental health/MBB FIMS final both tasks v7.sav") %>% dplyr::select(
   participant_id,
   secondary_id
)

microfims_missing_ids <- reliability_microfims %>% dplyr::filter(is.na(secondary_id)) %>% dplyr::select(participant_id) %>% dplyr::left_join(macrofims_ids, by = "participant_id")
```

