---
title: "microfims_long_dataset"
output: html_document
date: "2024-04-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup
## Load libraries
```{r}
library(tidyverse)
library(haven)
```

## Load and clean each dataset
Long format files for each participant for certification videos, tiebreaker videos, and all others
Column that identifies randomly assigned primary coder for videos that don't have tiebreakers and were not used in certification
### Tiebreaker codes
```{r}
# read in the certification videos, tiebreaker videos, and all others: each as their own separate list

# tiebreaker code directory
tiebreak_codes <- "../../FIMS/FIMS_micro_coding/MicroFIMS Core Team Training/microFIMS_reliability_data/behavior/tiebreaker_data/"

tiebreak_fl <- list.files(path=tiebreak_codes, pattern = "MBB_*", recursive=TRUE, full.names = TRUE)

read_tiebreaker_files <- function(fl) {
list_name <- "tiebreaker_code_dfs"
list <- list()
for (i in 1:length(fl)) { #for each file in the list
    #get info to add to the dfs
    id_file_name <- gsub(".*/(\\w+_(child|parent)).*", "\\1", fl[i]) #this is the participant id
    #read the file into r, create column names
    df <- read.table(fl[[i]], header=TRUE, fill=TRUE, sep=",")
    #set the df name to match the participant: <id_file_name>_<child|parent>
    df_name <- id_file_name
    #assign df to the list
    list[[i]] <- df 
    names(list)[i] <- df_name
  }
#assign the list to the global environment
assign(list_name, list, envir=.GlobalEnv)
}

#apply the function
read_tiebreaker_files(tiebreak_fl)

# get rid of extra columns and create secondary_id column
for (df_name in names(tiebreaker_code_dfs)) {
  #create secondary_id column
  tiebreaker_code_dfs[[df_name]] <- dplyr::mutate(tiebreaker_code_dfs[[df_name]], secondary_id := names(tiebreaker_code_dfs[df_name]))
  tiebreaker_code_dfs[[df_name]] <- dplyr::select(tiebreaker_code_dfs[[df_name]], secondary_id, contains("final"), relative_time)
  tiebreaker_code_dfs[[df_name]] <- dplyr::rename_with(tiebreaker_code_dfs[[df_name]], .fn = ~gsub("final", "primary", .), .cols = contains("final"))
}
```
## Certification codes
```{r}
consensus_codes <- "../../FIMS/FIMS_micro_coding/MicroFIMS Core Team Training/MicroFIMS expert behavior codes.xlsx"

#load data
multiplesheets(consensus_codes, "cons_codes") #load the consensus codes as a list of dfs, each df is a id_parent or _child

names_to_keep <- c("MBB_2_005_child", "MBB_2_005_parent", "MBB_2_036_child", "MBB_2_036_parent", "MBB_2_144_child", "MBB_2_144_parent")

# select only the files we want
certification_codes <- list()
for (df_name in names(cons_codes)) {
  if (df_name %in% names_to_keep) {
    certification_codes[[df_name]] <- cons_codes[[df_name]]
  }
}

#change the time variable to be double in all dfs
for (i in 1:length(certification_codes)) {
  if (is.character(certification_codes[[i]]$Time)) { #if the time variable is a character...
    certification_codes[[i]]$Time <- as.numeric(lubridate::hms(certification_codes[[i]]$Time)) #convert it to hh:mm:ss and then to numeric
  }
}

# change all of the codes to be lower case
for (df_name in names(certification_codes)) {
  certification_codes[[df_name]] <- dplyr::mutate(certification_codes[[df_name]], across(contains("Code"), ~str_to_lower(.), .names="{col}"))
}

# create the binary columns for each code
for (df_name in names(certification_codes)) {
#get column names that contain coders' codes
#create binary 'did the coder indicate this code' for each code
certification_codes[[df_name]] <- mutate(certification_codes[[df_name]], 
   across(`Consensus Code`, ~ifelse(grepl("neutral", .), 1, 0), .names="neutral_primary"),
   across(`Consensus Code`, ~ifelse(grepl("active", .), 1, 0), .names="active_primary"),
   across(`Consensus Code`, ~ifelse(grepl("positive", .), 1, 0), .names="positive_primary"),
   across(`Consensus Code`, ~ifelse(grepl("withdraw", .), 1, 0), .names="withdraw_primary"),
   across(`Consensus Code`, ~ifelse(grepl("off", .), 1, 0), .names="offtask_primary"),
   across(`Consensus Code`, ~ifelse(grepl("uncodable", .), 1, 0), .names="uncodable_primary"),
   across(`Consensus Code`, ~ifelse(grepl("auto", .), 1, 0), .names="nonauto_primary"),
   across(`Consensus Code`, ~ifelse(grepl("reject", .), 1, 0), .names="reject_primary")
) 
}

# get rid of extra columns and create secondary_id column
for (df_name in names(certification_codes)) {
  # rename consensus code column to be 'primary_codes'
  certification_codes[[df_name]] <- dplyr::rename(certification_codes[[df_name]], primary_codes = `Consensus Code`)
  #create secondary_id column
  certification_codes[[df_name]] <- dplyr::mutate(certification_codes[[df_name]], secondary_id := names(certification_codes[df_name]),
                                           relative_time = round(Time - Time[1], digits=0))
  certification_codes[[df_name]] <- dplyr::select(certification_codes[[df_name]], secondary_id, contains("primary"), relative_time)
  
}
```
## Other participants
```{r}
# load the file with assignment for coder1 or coder2 to be primary (validity dataset)
coder_assignment <- read_csv("data/microfims_validity_final_data.csv") %>% dplyr::select(secondary_id, primary_coder)

# load rest of second-by-second code files
path <- "../../FIMS/FIMS_micro_coding/MicroFIMS Core Team Training/microFIMS_reliability_data/behavior/" 

general_fl <- list.files(path=path, pattern = "*_agreement.csv", recursive=FALSE, full.names = TRUE)

read_general_files <- function(fl) {
list_name <- "general_code_dfs"
list <- list()
for (i in 1:length(fl)) { #for each file in the list
    #get info to add to the dfs
    id_file_name <- gsub(".*/(\\w+_(child|parent)).*", "\\1", fl[i]) #this is the participant id
    #read the file into r, create column names
    df <- read.table(fl[[i]], header=TRUE, fill=TRUE, sep=",")
    #set the df name to match the participant: <id_file_name>_<child|parent>
    df_name <- id_file_name
    #assign df to the list
    list[[i]] <- df 
    names(list)[i] <- df_name
  }
#assign the list to the global environment
assign(list_name, list, envir=.GlobalEnv)
}

#apply the function
read_general_files(general_fl)

# create binary code columns for each coder
for (df_name in names(general_code_dfs)) {
#get column names that contain coders' codes
coders <- colnames(general_code_dfs[[df_name]])[which(str_detect(colnames(general_code_dfs[[df_name]]), "_code$"))]
#create binary 'did the coder indicate this code' for each code
general_code_dfs[[df_name]] <- mutate(general_code_dfs[[df_name]], 
   across(ends_with("_code"), ~ifelse(grepl("neutral", .), 1, 0), .names="neutral_{sub('_code', '', col)}"),
   across(ends_with("_code"), ~ifelse(grepl("active", .), 1, 0), .names="active_{sub('_code', '', col)}"),
   across(ends_with("_code"), ~ifelse(grepl("positive", .), 1, 0), .names="positive_{sub('_code', '', col)}"),
   across(ends_with("_code"), ~ifelse(grepl("withdraw", .), 1, 0), .names="withdraw_{sub('_code', '', col)}"),
   across(ends_with("_code"), ~ifelse(grepl("off", .), 1, 0), .names="offtask_{sub('_code', '', col)}"),
   across(ends_with("_code"), ~ifelse(grepl("uncodable", .), 1, 0), .names="uncodable_{sub('_code', '', col)}"),
   across(ends_with("_code"), ~ifelse(grepl("auto", .), 1, 0), .names="nonauto_{sub('_code', '', col)}"),
   across(ends_with("_code"), ~ifelse(grepl("reject", .), 1, 0), .names="reject_{sub('_code', '', col)}")
) 
}

# rename coder columns to sub coder1 and coder2 for the coder initials
# coder1 is always the person with initials higher up the alphabet than coder 2
for (df_name in names(general_code_dfs)) {
  #create secondary_id column
  general_code_dfs[[df_name]] <- mutate(general_code_dfs[[df_name]], secondary_id := names(general_code_dfs[df_name]))
  # rename variables with <code>_<coder initials>
  general_code_dfs[[df_name]] <- rename_with(general_code_dfs[[df_name]],  ~gsub("..$", "coder1", .), .cols = ends_with("MA") | ends_with("CS"))
  general_code_dfs[[df_name]] <- rename_with(general_code_dfs[[df_name]],  ~gsub("..$", "coder2", .), .cols = ends_with("LL") | ends_with("SX"))
  # same thing but rename the variables with <coder initials>_code
  general_code_dfs[[df_name]] <- rename_with(general_code_dfs[[df_name]],  ~gsub("^..", "coder1", .), .cols = starts_with("MA") | starts_with("CS"))
  general_code_dfs[[df_name]] <- rename_with(general_code_dfs[[df_name]],  ~gsub("^..", "coder2", .), .cols = starts_with("LL") | starts_with("SX"))
  general_code_dfs[[df_name]] <- dplyr::select(general_code_dfs[[df_name]], secondary_id, contains("coder1"), contains("coder2"), relative_time)
  
}

# rename the appropriate columns to be 'primary' coder
# match secondary_id (minus _child or _parent) to the key doc to determine which end string to change to 'primary'
for (df_name in names(general_code_dfs)) {
  df_id <- gsub("_child|_parent", "", general_code_dfs[[df_name]]$secondary_id[1])
  primary_column <- as.character(coder_assignment[coder_assignment$secondary_id == df_id, "primary_coder"])
  general_code_dfs[[df_name]] <- rename_with(general_code_dfs[[df_name]],  ~gsub("_[^_]+$", "_primary", .), .cols = ends_with(primary_column))
  general_code_dfs[[df_name]] <- rename_with(general_code_dfs[[df_name]],  ~gsub("coder[12]_", "primary_", .), .cols = starts_with(primary_column))
}

# drop the non-primary codes
for (df_name in names(general_code_dfs)) {
  general_code_dfs[[df_name]] <- dplyr::select(general_code_dfs[[df_name]], secondary_id, contains("primary"), relative_time)
  general_code_dfs[[df_name]] <- dplyr::rename(general_code_dfs[[df_name]], primary_codes = primary_code)
}

# remove the participants who have tiebreaker data
general_code_dfs_final <- general_code_dfs[!names(general_code_dfs) %in% names(tiebreaker_code_dfs)]
```


# Overall Cleaning
## Combine the lists into one list now that they all share the same format
```{r}
all_code_dfs <- c(certification_codes, tiebreaker_code_dfs, general_code_dfs_final)
```

## Recode 'uncodable' seconds
If a given second is rated as uncodable, we want all of the other code columns to be 'NA'
```{r}
# recode rest of columns to be 'na' for any second coded as 'uncodable' 
for (df_name in names(all_code_dfs)) {
  all_code_dfs[[df_name]] <- dplyr::mutate(all_code_dfs[[df_name]], across(ends_with("primary") & !contains("uncodable"), ~ifelse(uncodable_primary==1, NA, .)))
}

# remove uncodable column
for (df_name in names(all_code_dfs)) {
  all_code_dfs[[df_name]] <- dplyr::select(all_code_dfs[[df_name]], secondary_id, relative_time, contains("primary") & !contains("uncodable"))
}

# weird that some of the dfs appear to show 10 columns in the list but then they actually have 9?? try merging and see if something weird happens
```

## Bind all of the dfs together into one df
```{r}
# bind rows all of the files together
long_df <- bind_rows(all_code_dfs)

#sum(long_df$secondary_id == "MBB_2_002_child")

#write_csv(long_df, "microfims_long_df_testing.csv")
```

## Merge parent and child columns for each participant
```{r}
# add _child or _parent to new column
long_df <- long_df %>% dplyr::mutate(dyad_member = sub(".*\\_", "", secondary_id))

# remove _parent from id
long_df$secondary_id <- gsub("_parent|_child", "", long_df$secondary_id)

# remove the _child and _parent from the dfs, add to new column 

# pivot wider
long_df_wide <- long_df %>% pivot_wider(
                         id_cols = c(secondary_id, relative_time),
                         names_from = c(dyad_member),
                         values_from = c(contains("primary")),
                         names_sep = "_")

```

# Write the output
```{r}
write_csv(long_df_wide, "data/microfims_long_dataset.csv")
```

